Data Analysis Expanded

### 2019-08-14 data_analysis/data_analysis_expanded.Rmd
Methods 2/4 started

@@

>>>>

## Method 2

```{r s1_m2_a}
# big grids and few partitions to start:
set.seed(12039)
s1_m2_a <- rre::cv_replicates(list_of_samples[[1]],
                              eval_function = "neg_unreg_like",
                              partitions = 5,
                              lambda_vec = seq(0,1000,by=200),
                              multiplier = 200,
                              c_seq_len = 20)
```
```{r s1_m2_a_print, results = 'asis'}
s1_m2_a %>% report_results_2(.)
```

```{r s2_m2_a}
# big grids and few partitions to start:
set.seed(12023439)
s2_m2_a <- rre::cv_replicates(list_of_samples[[2]],
                              eval_function = "neg_unreg_like",
                              partitions = 5,
                              lambda_vec = seq(0,1000,by=200),
                              multiplier = 200,
                              c_seq_len = 20)
```
```{r s2_m2_a_print, results = 'asis'}
s2_m2_a %>% report_results_2(.)
```

```{r s3_m2_a}
# big grids and few partitions to start:
set.seed(2342039)
s3_m2_a <- rre::cv_replicates(list_of_samples[[3]],
                              eval_function = "neg_unreg_like",
                              partitions = 5,
                              lambda_vec = seq(0,1000,by=200),
                              multiplier = 200,
                              c_seq_len = 20)
```
```{r s3_m2_a_print, results = 'asis'}
s3_m2_a %>% report_results_2(.)
```

<br><br>
<br><br>

@@

## Method 4

```{r s1_m4_a}
# big grids and few partitions to start:
set.seed(87124)
s1_m4_a <- rre::cv_replicates(list_of_samples[[1]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,1000,by=200),
                              multiplier = 200,
                              c_seq_len = 20)
```
```{r s1_m4_a_print, results = 'asis'}
s1_m4_a %>% report_results_2(.)
```

```{r s2_m4_a}
# big grids and few partitions to start:
set.seed(23456)
s2_m4_a <- rre::cv_replicates(list_of_samples[[2]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,1000,by=200),
                              multiplier = 200,
                              c_seq_len = 20)
```
```{r s2_m4_a_print, results = 'asis'}
s2_m4_a %>% report_results_2(.)
```

```{r s3_m4_a}
# big grids and few partitions to start:
set.seed(7654)
s3_m4_a <- rre::cv_replicates(list_of_samples[[3]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,1000,by=200),
                              multiplier = 200,
                              c_seq_len = 20)
```
```{r s3_m4_a_print, results = 'asis'}
s3_m4_a %>% report_results_2(.)
```

<br><br>
<br><br>
